### 2020-08-15 thesis/chap_1.tex
fix table

%\begin{table}[!htbp] \centering
\caption{AUC and average precision values for the predictions of the land use change model.} 
\label{tab:historic_metrics} 
\begin{tabular}{lcccc}
\hline
\hline
\multicolumn{1}{c}{Model} & \begin{tabular}[c]{@{}c@{}}Mean AUC\\ (Averaged \\ Surface)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Mean Precision\\ (Averaged \\ Surface)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Mean AUC +/- Std\\ (All iterations \\ averaged)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Mean Precision +/- Std\\ (All Iterations \\ averaged)\end{tabular} \\ \hline
\begin{tabular}[c]{@{}l@{}}Agricultural \\ Expansion\end{tabular} & $0.858$ & $0.383$ & $0.669 \pm 0.001$ & $0.105 \pm 0.001$ \\
Urbanisation & $0.784$ & $0.287$ & $0.618 \pm 0.001$ & $0.102 \pm 0.001$ \\ \hline
\end{tabular}
\end{table}

>>>>

%\begin{table}[!htbp] \centering
\caption{AUC and average precision values for the predictions of the land use change model.} 
\label{tab:historic_metrics} 
\begin{tabular}{lcccc}
\hline
\hline
\multicolumn{1}{c}{Model} & \begin{tabular}[c]{@{}c@{}}Mean AUC\\ (Averaged \\ Surface)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Mean Precision\\ (Averaged \\ Surface)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Mean AUC +/- Std\\ (All Iterations \\ Averaged)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Mean Precision +/- Std\\ (All Iterations \\ Averaged)\end{tabular} \\ \hline
\begin{tabular}[c]{@{}l@{}}Agricultural \\ Expansion\end{tabular} & $0.858$ & $0.383$ & $0.669 \pm 0.001$ & $0.105 \pm 0.001$ \\
Urbanisation & $0.784$ & $0.287$ & $0.618 \pm 0.001$ & $0.102 \pm 0.001$ \\ \hline
\end{tabular}
\end{table}
